### 2013-11-22 tests_Housing.Rmd
some extra data

```{r}
set.seed(304)

@@

########################################################
# Compare versions of GA.Poly (with vs without regularization)

source("gapolyfuncs.R")
report <- test.regularization(my.data, population=150, iterations=75, lambda=0.8, runs=50)

save(report, file="Housing300_lambda0.8.vs.no.reg_pop200.Rda") # recover with load("Housing300.Rda")

@@

write.table(df, "Housing300_lambda0.8.vs.no.reg_pop200.txt")

@@

########################################################
# Lambda Test (2nd variant of regularization)
size <- 31
lambda.values <- rep(NA, size)

val <- 0.001
for(i in 1:size) {
  lambda.values[i] = val
  val = val * 2^(1/3)  # duplicate every three steps
}

n.runs <- 5

source("gapolyfuncs.R")
errors <- test.lambda(my.data, lambda.values, runs=n.runs, population=5, iterations=15)

>>>>

```{r}
set.seed(121)

@@

########################################################
# Compare versions of GA.Poly (with vs without regularization)
set.seed(765)
source("gapolyfuncs.R")
report <- test.regularization(my.data, population=300, iterations=75, lambda=0.01, runs=10)

save(report, file="Housing300_lambda0.01.vs.no.reg2_2.Rda")  
# report <- load("Housing300_lambda0.01.vs.no.reg2_1.Rda")  # recover with

@@

write.table(df, "Housing300_lambda0.01.vs.no.reg2_2.txt")

@@

########################################################
# Lambda Test (2nd variant of regularization)
size <- 20
lambda.values <- rep(NA, size)

val <- 0.003
for(i in 1:size) {
  lambda.values[i] = val
  val = val * 2^(1/3)  # duplicate every three steps
}

n.runs <- 10

source("gapolyfuncs.R")
errors <- test.lambda(my.data, lambda.values, runs=n.runs, population=50, iterations=40)
